---
title: "Condition factor"
output: html_notebook
---

Growth parameter descriptions:
After embryos were exposed to NAFCs, they were moved to outdoor mesocosms filled with clean lake water and raised in the mesocosms for 1 month. At the end of the month, larvae were removed, measured for wet mass (mg) and measured for length (mm) using photography and ImageJ. Larvae Condition factor was then calculated using Fulton's K formula (K= 100*(W/L^3)). 

Random effects included in lmer model for growth parameters include:
Section: Where mesocosms were located in outdoor setup (there were 3 sections labelled 1,2,3, see overview sheet for diagram)
FishInMesoStart: Initial stocking density for individual mesocosms
FishInMesoEnd: Density of fish in individual mesocosm at end of experiment 

Loading data:
```{r}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(lme4)

growthdata<-read.csv("/Users/jreyn/OneDrive/Documents/grad school/NAFHM19/Data/analysis/aug21growthR.csv")
growthdata$Rep<- as.factor(growthdata$Rep)
growthdata$Section<- as.factor(growthdata$Section)
growthdata
```

Checking assumptions for CF lm analysis:

```{r}
CFmodel<- lm(CF ~ Treatment, data= growthdata)
plot(CFmodel)
plot(CFmodel, 4)
```
I think Q-Q, residuals vs fitted, scale-location, and cook's distance on all points looks good, do not think data needs to be adjusted. 

Using backwards stepwise regression to determing if random effects influence model:

```{r}
CFmodel<- lmer(CF ~ Treatment + (Treatment|Rep) + (Treatment|Section)+ (Treatment|FishInMesoEnd)+ (Treatment|FishInMesoStart), data=growthdata)
CFmodel1<- lmer(CF ~ Treatment + (1|Rep) + (Treatment|Section)+ (Treatment|FishInMesoEnd)+ (Treatment|FishInMesoStart), data=growthdata)
#notsignificant anova(CFmodel, CFmodel1)
CFmodel2<-lmer(CF ~ Treatment + (1|Rep) + (1|Section)+ (Treatment|FishInMesoEnd)+ (Treatment|FishInMesoStart), data=growthdata)
#not significant anova(CFmodel1, CFmodel2)
CFmodel3<- lmer(CF ~ Treatment + (1|Rep) + (1|Section)+ (1|FishInMesoEnd)+ (Treatment|FishInMesoStart), data=growthdata)
#notsignificant anova(CFmodel2, CFmodel3)
CFmodel4<- lmer(CF ~ Treatment + (1|Rep) + (1|Section)+ (1|FishInMesoEnd)+ (1|FishInMesoStart), data=growthdata)
#notsignificant anova(CFmodel3, CFmodel4)
CFmodel5<- lmer(CF ~ Treatment +  (1|Rep) + (1|Section)+ (1|FishInMesoEnd), data=growthdata)
anova(CFmodel4, CFmodel5)
#significant anova(CFmodel4, CFmodel5), FishMesoStart affects model
CFmodel6<- lmer(CF ~ Treatment + (1|Rep) + (1|Section)+ (1|FishInMesoStart), data=growthdata)
anova(CFmodel4, CFmodel6)
#significant anova(CFmodel4, CFmodel6), FishMesoEnd affects model
CFmodel7<- lmer(CF ~ Treatment + (1|Rep) +  (1|FishInMesoEnd)+ (1|FishInMesoStart), data=growthdata)
#notsignificant anova(CFmodel4, CFmodel7)
CFmodel8<- lmer(CF ~ Treatment + (1|FishInMesoEnd)+ (1|FishInMesoStart), data=growthdata)
anova(CFmodel7, CFmodel8)
#significant anova(CFmodel7, CFmodel8), Rep affects model
CFmodel9<- lmer(CF ~ 1 + (1|Rep) +  (1|FishInMesoEnd)+ (1|FishInMesoStart), data=growthdata)
anova(CFmodel7, CFmodel9)
#notsignificant! anova(CFmodel7, CFmodel9), Treatment does not affect CF but replicate and fish densities do 
```
Embryonic NAFC treatment does not significantly affect larval condition factor (p= 0.2985), but replicate (p= 0.01605*), fish stocking density (p= 0.0002385***) and fish density at the end (p= 2.541e-06***) do. 










