---
title: "Figure 4a Larval mortality"
output: html_notebook
---
Loading data.
Labels:
Section: Where mesocosms were located in outdoor setup (there were 3 sections labelled 1,2,3, see overview sheet for diagram)
DeadAlive: Larval mortality, 1= Dead, 0=Alive
FishInMesoStart: Initial stocking density for individual mesocosms
FishInMesoEnd: Density of fish in individual mesocosm at end of experiment 
```{r}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(lme4)
lmortdata<- read.csv("/Users/jreyn/OneDrive/Documents/grad school/NAFHM19/Data/analysis/mortalityGLM.csv")
lmortdata$Rep<- as.factor(lmortdata$Rep)
lmortdata$Section<- as.factor(lmortdata$Section)
lmortdata
```


Checking assumptions for glm analysis:

```{r}
lmortmodel<- glm(DeadAlive ~ Treatment, data= lmortdata, family=binomial)
plot(lmortmodel)
plot(lmortmodel, 4)
```
**Scale location and residuals vs fitted are fairly flat. Normal Q-Q plot does not follow a 1:1 trend, however, unsure how to transform binary data. **


Backwards stepwise regression to test significance of random factors:
```{r}
m1 = glmer(DeadAlive ~ Treatment + (1|Rep) + (1|Section)+ (1|FishInMesoStart)+ (1|FishInMesoEnd), data= lmortdata, family=binomial)
m2 = glmer(DeadAlive ~ Treatment + (1|Section)+ (1|FishInMesoStart)+ (1|FishInMesoEnd), data= lmortdata, family=binomial)
#not significant anova(m1, m2), Rep does not affect model
m3 = glmer(DeadAlive ~ Treatment + (1|Section)+ (1|FishInMesoStart), data= lmortdata, family=binomial)
# not significant anova(m2, m3), FishInMesoEnd does not affect model
m4 = glmer(DeadAlive ~ Treatment + (1|Section), data= lmortdata, family=binomial)
#not significant anova(m3,m4)m FishInMesoStart does not affect model
m5=  glm(DeadAlive ~ Treatment , data= lmortdata, family=binomial)
#notsignificant anova(m4,m5), Section does not affect model
summary(m5)
```
Embryonic NAFC treatment significantly affects larval mortality (p=0.000467 ***)

Larval mortality LC50 calculation:

```{r}
dose.p(lmortmodel, p = c(0.5))

```

LC50 for larval mortality is 36.72 mg/L
**Can 95% confidence intervals be calculated using the standard error?**

Plotting glm:

***Will improve this graphs to include proportion of mortality**
```{r}
range(lmortdata$Treatment)
xTreatment <- seq(0, 21, 0.01)

```
```{r}
yTreatment<- predict(lmortmodel, list(Treatment = xTreatment),type="response")
plot(lmortdata$Treatment, lmortdata$DeadAlive, pch= 16, xlab= "Embryonic NAFC treatment (mg/L)", ylab= "Mortality")
lines(xTreatment, yTreatment, lwd = 2)
abline(v= 36.72, lty= 2, lwd= 3)
```





