---
title: "Figure 2a EmbryoMortality"
output: html_notebook
---

Loading data:
```{r}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(lme4)
library(MASS)
library(drc)

#embryo mortality data
emortdata<- read.csv("/Users/jreyn/OneDrive/Documents/grad school/NAFHM19/Data/analysis/EmbryoMort1.csv")
emortdata$Rep<- as.factor(emortdata$Rep)
emortdata
tail(emortdata)
```

Checking assumptions for glm analysis:

```{r}
emortmodel<- glm(Mortality ~ Treatment, data= emortdata, family=binomial)
plot(emortmodel)
plot(emortmodel, 4)
```
Residuals vs fitted and scale location look fairly flat lined, and normal Q-Q plot looks to follow 1:1 trend. 

***Would love your thoughts and second opinion on checking the assumptions of the data**

Glmer backwards stepwise regression to test if random effects are significant:
```{r}
m1<- glmer(Mortality~ Treatment + (Treatment|Rep), data= emortdata, family=binomial)
m2<- glmer(Mortality~ Treatment + (1|Rep), data= emortdata, family=binomial)
#anova(m1, m2)
#not significant, no interaction between treatment and rep
m3<- glm(Mortality~ Treatment, data= emortdata, family=binomial)
#anova(m2, m3)
#not signficant, Rep does not affect model
summary(m3)
```
Treatment significantly affects embryo mortality (p=<2e-16 ***)


```{r}
emortmodel<- glm(Mort ~ ï..Treatment, data= emortdata, family=binomial)
summary(emortmodel)
```
When replicate is taken out of model, NAFC treatment significantly affects embryo mortality (p = 2e-16 ***). 


Embryo mortality LC50 calculation:

```{r}
dose.p(emortmodel, p = c(0.5))

```
LC50 for embryo mortality is 20.22 mg/L NAFC.

***QUESTION: Is it possible to calculate 95% CI of this LC50 with the SE?*** 

Plotting the glm with LC50:
```{r}
range(emortdata$Treatment)
xETreatment <- seq(0, 53.8, 0.01)
```

***As discussed, the below figure could use much improvement. Will make y-axis proportion of mortality, and either use bar graph or point graph to represent average proportion of mortality (across 3 reps) for each treatment, then place glm curve with LC50 over top.***

```{r}
yETreatment<- predict(emortmodel, list(Treatment = xETreatment),type="response")
plot(emortdata$Treatment, emortdata$Mortality, pch= 16, xlab= "Embryonic NAFC treatment (mg/L)", ylab= "Mortality")
lines(xETreatment, yETreatment,lwd = 2)
abline(v= 18.75124, lty= 2, lwd= 1)
```









