---
title: "Figure 2d EmbryonicTwitches"
output: html_notebook
---

```{r}
#embryo twitches
library(dplyr)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(lme4)
etwitchdata<- read.csv("/Users/jreyn/OneDrive/Documents/grad school/NAFHM19/Data/analysis/EmbryoTwitches.csv")
etwitchdata$Rep<- as.factor(etwitchdata$Rep)
etwitchdata

```

Checking assumptions for lm analysis:

```{r}
etwitchmodel<-lm(Twitch ~ 誰..Treatment, data=etwitchdata)
plot(etwitchmodel)
plot(etwitchmodel, 4)
```
***Could use some help making some decisions about these assumptions. For example, the normal Q-Q plot shows mostly normal distribution, with exception of points 57 and 56. Do these points have a far enough away cook's distance to be considered outliers that should be removed from data set? **

lmer backwards stepwise regression to test if random effects are significant:

```{r}
m1<- lmer(Twitch~ 誰..Treatment + (1|Rep), data= etwitchdata)
m2<- lm(Twitch~ 誰..Treatment, data= etwitchdata)
anova(m1, m2)
#no significant difference between models, rep does not influence hatch  viability
summary(m2)
```
Embryonic NAFC treatment significantly reduced embryonic heart rate (p=1.68e-09 ***)

Graphing twitch data:
```{r}
ggplot(etwitchdata, aes(x=誰..Treatment, y= Twitch))+ 
         geom_point()+
         geom_smooth(method='lm', colour= "black")+
  ylab('Twitches')+ xlab('Embryonic NAFC treatment (mg/L)')+
  theme_few()

```













