---
title: "Figure 2e Embryonic dry mass"
output: html_notebook
---

***This graph was not included in manuscript but is reported in results**

Loading data: 
```{r}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(lme4)
emassdata<- read.csv("/Users/jreyn/OneDrive/Documents/grad school/NAFHM19/Data/analysis/EmbryoMass.csv")
emassdata$Rep<- as.factor(emassdata$Rep)
emassdata
```

Checking assumptions for lm analysis:

```{r}
emassmodel<-lm(Mass.embryo.mg. ~ Treatment, data=emassdata)
plot(emassmodel)
plot(emassmodel, 4)
```
Residuals vs fitted is fairly flat, as is scale location. Normal Q-Q plot follows 1:1 trend for most part, but would be interested on your thoughts if points 11, 12, and 23 may skew normaility too much. No residuals seem to have a cook's distance greater than 3. 


lmer backwards stepwise regression to test if random effects are significant:

```{r}
m1<- lmer(Mass.embryo.mg.~ Treatment + (1|Rep), data= emassdata)
m2<- lm(Mass.embryo.mg.~ Treatment, data= emassdata)
#no significant difference between models, rep does not influence hatch  viability
summary(m2)
```
Embryonic mass was not significantly influenced by embryonic NAFC treatment (p=0.0999). 


Graphing mass data:
```{r}
ggplot(emassdata, aes(x=Treatment, y= Mass.embryo.mg.))+ 
         geom_point()+
         geom_smooth(method='lm', colour= "black")+
  ylab('Embryo mass (mg/L)')+ xlab('Embryonic NAFC treatment (mg/L)')+
  theme_few()

```





