---
title: "Figure 2b EmbryoHatchViabilitty"
output: html_notebook
---

Loading data:
```{r}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(lme4)

#embryo hatch viability data
ehatchdata<- read.csv("/Users/jreyn/OneDrive/Documents/grad school/NAFHM19/Data/analysis/EmbryoHatchViability1.csv")
ehatchdata$Rep<- as.factor(ehatchdata$Rep)
ehatchdata
```

Checking assumptions for glm analysis:

```{r}
ehatchmodel<- glm(Viability ~ ï..Treatment, data= ehatchdata, family=binomial)
plot(ehatchmodel)
plot(ehatchmodel, 4)
```

Scale-location and residuals vs leverage plots have horizontal lines, and no residuals are more than 3 cook's distance away. Data looks fairly normal?



Glmer backwards stepwise regression to test if random effects are significant:

```{r}
m1<- glmer(Viability~ ï..Treatment + (ï..Treatment|Rep), data= ehatchdata, family=binomial)
m2<- glmer(Viability~ ï..Treatment + (1|Rep), data= ehatchdata, family=binomial)
#not significant, anova(m1, m2), no mixed effect between treatment and rep
m3<- glm(Viability~ ï..Treatment, data= ehatchdata, family=binomial)
#anova(m2,m3)
#no significant difference between models, rep does not influence hatch  viability
summary(m3)
```
Embryonic NAFC treatment signficantly affects embryonic hatch viability (p=   <2e-16 ***)

Embryo hatch viability EC50 calculation:
```{r}
ehatchmodel<- glm(Viability ~ ï..Treatment, data= ehatchdata, family=binomial)
dose.p(ehatchmodel, p = c(0.5))
```
EC50 for embryo hatch viability is 21.13 mg/L NAFC.

Plotting the glm with EC50:
```{r}
range(ehatchdata$ï..Treatment)
xEHTreatment <- seq(0, 54, 0.01)

```

***As discussed, the below figure could use much improvement. Will make y-axis proportion of hatch viability, and either use bar graph or point graph to represent average proportion of hatches (across 3 reps) for each treatment, then place glm curve with EC50 over top.***

```{r}
yEHTreatment<- predict(ehatchmodel, list(ï..Treatment = xEHTreatment),type="response")
plot(ehatchdata$ï..Treatment, ehatchdata$Viability, pch= 16, xlab= "Embryonic NAFC treatment (mg/L)", ylab= "Hatch viability")
lines(xEHTreatment, yEHTreatment,lwd = 2)
abline(v= 18.75124, lty= 2, lwd= 1)
```










