---
title: "Figure 2c heart rate"
output: html_notebook
---

Loading data:
```{r}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(lme4)
#embryo heart rate
eheartdata<- read.csv("/Users/jreyn/OneDrive/Documents/grad school/NAFHM19/Data/analysis/EmbryoHeartbeat.csv")
eheartdata$Rep<- as.factor(eheartdata$Rep)
eheartdata
```

Checking assumptions for lm analysis:

```{r}
eheartmodel<-lm(Avg.Heartbeat ~ 誰..Treatment, data=eheartdata)
plot(eheartmodel)
plot(eheartmodel, 4)
```
Residuals vs fitted and scale location look fairly flat lined, and normal Q-Q plot looks to follow 1:1 trend. No residuals are more than 3 cooks distance away. 

lmer backwards stepwise regression to test if random effects are significant:

```{r}
m1<- lmer(Avg.Heartbeat~ 誰..Treatment + (1|Rep), data= eheartdata)
m2<- lm(Avg.Heartbeat~ 誰..Treatment, data= eheartdata)
anova(m1, m2)
#no significant difference between models, rep does not influence heart beat
summary(m2)
```
Embryonic NAFC treatment significantly affects average embryonic heart rate (p=2.28e-12 ***). 

***dose.p function from MASS package does not work for non-binary data sets, need to figure out a way to calculate IC10 for heart rate using linear model***

Graphing:

Embryo heart rate:
```{r}
ggplot(eheartdata, aes(x=誰..Treatment, y= Avg.Heartbeat))+ 
         geom_point()+
         geom_smooth(method='lm', colour= "black")+
  ylab('Heart rate (min)')+ xlab('Embryonic NAFC treatment (mg/L)')+
  theme_few()

```






















