---
title: "Length"
output: html_notebook
---

Growth parameter descriptions:
After embryos were exposed to NAFCs, they were moved to outdoor mesocosms filled with clean lake water and raised in the mesocosms for 1 month. At the end of the month, larvae were removed, measured for wet mass (mg) and measured for length (mm) using photography and ImageJ. Larvae Condition factor was then calculated using Fulton's K formula (K= 100*(W/L^3)). 

Random effects included in lmer model for growth parameters include:
Section: Where mesocosms were located in outdoor setup (there were 3 sections labelled 1,2,3, see overview sheet for diagram)
FishInMesoStart: Initial stocking density for individual mesocosms
FishInMesoEnd: Density of fish in individual mesocosm at end of experiment 

Loading data:
```{r}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(lme4)

growthdata<-read.csv("/Users/jreyn/OneDrive/Documents/grad school/NAFHM19/Data/analysis/aug21growthR.csv")
growthdata$Rep<- as.factor(growthdata$Rep)
growthdata$Section<- as.factor(growthdata$Section)
growthdata
```


Checking assumptions for length lm analysis:

```{r}
lengthmodel<- lm(Length ~ Treatment, data= growthdata)
plot(lengthmodel)
plot(lengthmodel, 4)
```
I think Q-Q, residuals vs fitted, scale-location, and cook's distance on all points looks good, do not think data needs to be adjusted. 

Using backwards stepwise regression to determing if random effects influence model:
```{r}
lengthmodel<- lmer(Length ~ Treatment + (Treatment|Rep) + (Treatment|Section)+ (Treatment|FishInMesoEnd)+ (Treatment|FishInMesoStart), data=growthdata)
lengthmodel1<- lmer(Length ~ Treatment + (1|Rep) + (Treatment|Section)+ (Treatment|FishInMesoEnd)+ (Treatment|FishInMesoStart), data=growthdata)
#notsignificant anova(lengthmodel, lengthmodel1)
lengthmodel2<- lmer(Length ~ Treatment + (1|Rep) + (1|Section)+ (Treatment|FishInMesoEnd)+ (Treatment|FishInMesoStart), data=growthdata)
#notsignificant anova(lengthmodel1, lengthmodel2)
lengthmodel3<- lmer(Length ~ Treatment + (1|Rep) + (1|Section)+ (1|FishInMesoEnd)+ (Treatment|FishInMesoStart), data=growthdata)
#notsignifcant anova(lengthmodel2, lengthmodel3)
lengthmodel4<- lmer(Length ~ Treatment + (1|Rep) + (1|Section)+ (1|FishInMesoEnd)+ (1|FishInMesoStart), data=growthdata)
#notsignificant anova(lengthmodel3, lengthmodel4)
lengthmodel5<- lmer(Length ~ Treatment + (1|Rep) + (1|Section)+ (1|FishInMesoEnd), data=growthdata)
anova(lengthmodel4, lengthmodel5)
#significant anova(lengthmodel4, lengthmodel5), FishInMesoStart affects model
lengthmodel6<- lmer(Length ~ Treatment + (1|Rep) + (1|Section)+ (1|FishInMesoStart), data=growthdata)
anova(lengthmodel4, lengthmodel6)
#signficant anova(lengthmodel4, lengthmodel6), FishInMesoEnd affects model
lengthmodel7<- lmer(Length ~ Treatment + (1|Rep) + (1|FishInMesoEnd)+ (1|FishInMesoStart), data=growthdata)
anova(lengthmodel4, lengthmodel7)
#significant anova(lengthmodel4, lengthmodel7), Section affects model
lengthmodel8<- lmer(Length ~ Treatment  + (1|Section)+ (1|FishInMesoEnd)+ (1|FishInMesoStart), data=growthdata)
#notsignificant anova(lengthmodel4, lengthmodel8)
lengthmodel9<- lmer(Length ~ 1  + (1|Section)+ (1|FishInMesoEnd)+ (1|FishInMesoStart), data=growthdata)
anova(lengthmodel8, lengthmodel9)
#notsignificant anova(lengthmodel8, lengthmodel9), treatment does not affect length
```
Embryonic NAFC treatment does not significantly affect larval length (p= 0.1624), but section (p=  0.001661), fish stocking density (p= 0.005376) and fish density at the end (p= 6.224e-05) do. 












