---
title: "Mass"
output: html_notebook
---

Growth parameter descriptions:
After embryos were exposed to NAFCs, they were moved to outdoor mesocosms filled with clean lake water and raised in the mesocosms for 1 month. At the end of the month, larvae were removed, measured for wet mass (mg) and measured for length (mm) using photography and ImageJ. Larvae Condition factor was then calculated using Fulton's K formula (K= 100*(W/L^3)). 

Random effects included in lmer model for growth parameters include:
Section: Where mesocosms were located in outdoor setup (there were 3 sections labelled 1,2,3, see overview sheet for diagram)
FishInMesoStart: Initial stocking density for individual mesocosms
FishInMesoEnd: Density of fish in individual mesocosm at end of experiment 

Loading data:
```{r}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(lme4)

growthdata<-read.csv("/Users/jreyn/OneDrive/Documents/grad school/NAFHM19/Data/analysis/aug21growthR.csv")
growthdata$Rep<- as.factor(growthdata$Rep)
growthdata$Section<- as.factor(growthdata$Section)
growthdata
```


Checking assumptions for mass lm analysis:

```{r}
massmodel<- lm(Mass ~ Treatment, data= growthdata)
plot(massmodel)
plot(massmodel, 4)
```

I think Q-Q, residuals vs fitted, scale-location, and cook's distance on all points looks good, do not think data needs to be adjusted. 


Using backwards stepwise regression to determing if random effects influence model:


```{r}
massmodel<- lmer(Mass ~ Treatment + (Treatment|Rep) + (Treatment|Section)+ (Treatment|FishInMesoEnd)+ (Treatment|FishInMesoStart), data=growthdata)
massmodel1<- lmer(Mass ~ Treatment + (1|Rep) + (Treatment|Section)+ (Treatment|FishInMesoEnd)+ (Treatment|FishInMesoStart), data=growthdata)
#not significant anova(massmodel, massmodel1)
massmodel2<- lmer(Mass ~ Treatment + (1|Rep) + (1|Section)+ (Treatment|FishInMesoEnd)+ (Treatment|FishInMesoStart), data=growthdata)
#notsignficant anova(massmodel1, massmodel2)
massmodel3<- lmer(Mass ~ Treatment + (1|Rep) + (1|Section)+ (1|FishInMesoEnd)+ (Treatment|FishInMesoStart), data=growthdata)
#notsignficant anova(massmodel2, massmodel3)
massmodel4<- lmer(Mass ~ Treatment + (1|Rep) + (1|Section)+ (1|FishInMesoEnd)+ (1|FishInMesoStart), data=growthdata)
#notsignificant anova(massmodel3, massmodel4)
massmodel5<- lmer(Mass ~ Treatment + (1|Rep) + (1|Section)+ (1|FishInMesoEnd), data=growthdata)
anova(massmodel4, massmodel5)
#signficant anova(massmodel4, massmodel5), FishInMesoStart affects model
massmodel6<- lmer(Mass ~ Treatment + (1|Rep) + (1|Section)+ (1|FishInMesoStart), data=growthdata)
anova(massmodel4, massmodel6)
#signficant anova(massmodel4, massmodel6), FishInMesoEnd affects model
massmodel7<- lmer(Mass ~ Treatment + (1|Rep) +  (1|FishInMesoEnd)+ (1|FishInMesoStart), data=growthdata)
anova(massmodel4, massmodel7)
#signficant anova(massmodel4, massmodel7), Section affects model
massmodel8<- lmer(Mass ~ Treatment + (1|Section)+ (1|FishInMesoEnd)+ (1|FishInMesoStart), data=growthdata)
#notsignifant anova(massmodel4, massmodel8)
massmodel9<- lmer(Mass ~ 1 + (1|Section)+ (1|FishInMesoEnd)+ (1|FishInMesoStart), data=growthdata)
anova(massmodel8, massmodel9)
#notsignificant anova(massmodel8, massmodel9), treatment does not affect mass 
```

Embryonic NAFC treatment does not significantly affect larval length (p=   0.5583), but section (p=  0.003327 **), fish stocking density (p= 8.68e-05 ***) and fish density at the end (p= 3.789e-08 ***) do. 






















